Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
more

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
\cite{GeDeM-CAV-09}
A instantiation-based procedure is shown in~ to be complete for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all occurrences of variables occur as direct subchildren of uninterpreted functions.
For example, the formula $\forall x\typ{\sortint}.\;\, \con{f}( x ) \teq g( x ) + 5$ 
is in the essentially uninterpreted fragment since all occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and $g$.
Other syntactic criteria are identified in this paper that extend this fragment slightly, including cases when variables occur as arguments of arithmetic predicates.
The techniques in~\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified formulas over uninterpreted types as well as types having a 
fixed finite interpretation (such as fixed-width bitvectors, datatype enumerations, etc.).
For example, finite model finding techniques can find a model for
the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, \neg x \teq y \vee \con{f}( x ) \teq \con{f}( y )$
where the uninterpreted type $\tau$ is interpreted as a finite set, and $\con{f}$ as injective finite map.

>>>>

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
Ge and de Moura \cite{GeDeM-CAV-09} presented a complete instantiation-based
procedure for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all
occurrences of variables occur as direct subterms of uninterpreted
functions. For example, the formula $\forall x%\typ{\sortint} --- the sort is not important, right?
.\;\, \con{f}( x )
\teq \con{g}( x ) + 5$ is in the essentially uninterpreted fragment.
% since all
% occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and
% $\con{g}$.
Other syntactic criteria are identified in this paper that extend
this fragment slightly, including cases when variables occur as arguments of
arithmetic predicates. The techniques in~Reynolds et al.\
\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified
formulas over uninterpreted types as well as types having a fixed finite
interpretation, such as fixed-width bitvectors and enumerated datatypes.
Finite model finding techniques can
find a model for the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, \neg x \teq
y \vee \con{f}( x ) \teq \con{f}( y )$ where the uninterpreted type $\tau$ is
interpreted as a finite set and $\con{f}$ as injective finite map.
\jb{Weird example. This formula is a tautology of EUF! Maybe you put the
negation at the right place?}
